A meta-analysis of mental rotation ability in the first years of life

### 2022-04-26 code/analysis.Rmd
Tweak regression models and plot

    # Gender as a categorical (factor) variable
    gender_f = case_when(
      female_percent == 1.0 ~ "Female",
      female_percent == 0.0 ~ "Male",
      TRUE ~ "Mixed"
    ) %>% factor(levels = c("Mixed", "Female", "Male")),
    # Re-code as contrast for the meta-regression model
    gender = recode(gender_f, "Mixed" = 0, "Female" = -0.5, "Male" = 0.5),

@@

    # Task type as a categorical (factor) variale
    task_f = factor(task, levels = c("Habituation", "VoE")),
    # Re-code as contrast for the meta-regression model
    task = recode(task_f, "Habituation" = -0.5, "VoE" = 0.5),
    .keep = "unused"
  ) -> dat_reg

@@

```{r, fig_regression}
# Plot regression with gender and age
alph <- 0.7
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi, color = gender_f)) +
  # Data points
  # geom_errorbar(aes(xmin = age - age_sd, xmax = age + age_sd), alpha = alph) +
  # geom_errorbar(aes(ymin = gi - sei, ymax = gi + sei), alpha = alph) +
  geom_point(aes(size = ni), shape = 16, alpha = alph) +
  # Regression lines - currently not reflecting the meta-analytic model
  geom_smooth(method = lm, formula = y ~ x, alpha = .1) +
  # Styling
  scale_x_continuous(limits = c(3, 16), breaks = seq(4, 16, 2)) +
  scale_y_continuous(limits = c(-1.3, 2.5), breaks = seq(-1, 2.5, 0.5)) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    color = "Gender",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    panel.border = element_rect(size = 1),
    panel.grid = element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  )

# Save the plot
ggsave(here(figures_dir, "regression.pdf"), width = 7, height = 4)
```

>>>>

    # Gender as a categorical (factor) variable
    gender = case_when(
      female_percent == 1.0 ~ "Female",
      female_percent == 0.0 ~ "Male",
      TRUE ~ "Mixed"
    ) %>% factor(levels = c("Mixed", "Female", "Male")),

@@

    # Task type as a categorical (factor) variale
    task = factor(task, levels = c("Habituation", "VoE")),

    # Combine gender and task into one column for plotting
    gender_task = factor(
      str_c(gender, task, sep = ", "),
      levels = c(
        "Female, Habituation",
        "Male, Habituation",
        "Mixed, Habituation",
        "Mixed, VoE"
      )
    )
  ) -> dat_reg

# Set numerical contrasts for factor variables
contrasts(dat_reg$gender) <- MASS::contr.sdif(3)
contrasts(dat_reg$task) <- MASS::contr.sdif(2)

@@

```{r, fig_regression}
# Get draws from the posterior distribution
draws_reg <- epred_draws(
  res_brm_reg,
  dat_reg,
  ndraws = n_draws,
  re_formula = NA
)

# Use colors as proposed in https://arxiv.org/abs/2107.02270
habi_colors <- c(
  "Female, Habituation" = "#5790fc",
  "Male, Habituation" = "#f89c20",
  "Mixed, Habituation" = "#e42536"
)
voe_colors <- c("Mixed, VoE" = "#964a8b")

# Regression plot
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = 0, linetype = "dashed") +

  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habituation_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +

  # Regression lines and HPDIs - VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    fill = NA,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(
    color = guide_legend(
      title = "Violation of\nexpectation tasks"
    ),
    order = 2
  ) +

  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.9, end = 0.7,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "Bayesian HPDI",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    legend.key = element_blank(),
    panel.border = element_rect(size = 1),
    panel.grid = element_blank(), # element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  )

# Save the plot
ggsave(here(figures_dir, "regression.pdf"), width = 8, height = 5)
```
